Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-06-02 article.rnw
a few more minor tweaks

One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{mccann1998weak,neutel2002stability,wootton2016many}, and setting any individual parameter to zero risks losing important information.
Another approach assumes that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.

@@

% DBS: We need to add a reference to the partial residual plots in the supps.

>>>>

One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives, weiss2021disentangling}.
However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{mccann1998weak,neutel2002stability,wootton2016many}. Setting any individual parameter to zero thus risks losing important information; moreover, we often do not know with confidence which parameters are likely to be zeros and which are not.
Another approach assumes that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species}.

@@

% DBS: As per my comment immediately above, we need to add a reference to the partial residual plots in the supps.
